### 2022-07-26 README.Rmd
Adjustments to readme and dependencies in DESCRIPTION

## Example
This is a real data example which produces 5000 simulations from a synchronized time scale.
```{r example, message=FALSE, warning=FALSE, include=FALSE}
require(INLA)
library(bremla)
data("event_intervals")
data("events_rasmussen")
data("NGRIP_5cm")

@@

gg2 = gg2 + geom_segment(data=data.frame(depth=x$data$depth[tie_indexes],                                          median=x$simulation$summary_sync$median[tie_indexes]-ageref_tie,                               lower=x$simulation$summary_sync$lower[tie_indexes]-ageref_tie,
                    upper=x$simulation$summary_sync$upper[tie_indexes]-ageref_tie),
                    aes(x=.data$depth,y=.data$lower,xend=.data$depth,yend=.data$upper),
                    col="magenta")
print(gg2)
```   
## Attribution

>>>>

## Example
This is a real data example which produces 5000 simulations from a synchronized time scale.
```{r example, message=FALSE, warning=FALSE, include=TRUE}
require(INLA)
library(bremla)
data("event_intervals")
data("events_rasmussen")
data("NGRIP_5cm")

@@

gg2 = gg2 + geom_segment(data=data.frame(depth=x$data$depth[tie_indexes],                                          median=x$simulation$summary_sync$median[tie_indexes]-ageref_tie,                               lower=x$simulation$summary_sync$lower[tie_indexes]-ageref_tie,
                    upper=x$simulation$summary_sync$upper[tie_indexes]-ageref_tie),
                    aes(x=.data$depth,y=.data$lower,xend=.data$depth,yend=.data$upper),
                    col="magenta")
print(gg2)
```

## Attribution
